Explore the SingleR results

### 2025-08-15 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/singler-results.Rmd

### Distirbution of cell types

@@

PDX samples have, not unexpectedly, much less cell type diversity overall with most cells being tumor or similar and immune cells rarely present.
This is consistent with expectations in general for the biology of PDX's.

@@

This section shows a heatmap compaing SingleR annotations to consensus cell types, for PDX samples only.

>>>>

@@

PDX samples have, not unexpectedly, much less cell type diversity overall with most cells being tumor or similar and immune cells rarely present.
This is consistent with expectations in general for the biology of PDX samples.

@@

This section shows a heatmap comparing SingleR annotations to consensus cell types, for PDX samples only.
